Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction

### 2024-03-10 paper/remotesensing-2870812-english.tex
more paper updates

 The robotic team presented in this study consists of two key sensing sentinels: an uncrewed surface vessel (USV) used to collect in situ reference measurements and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products. Both platforms are coordinated using open source \hl{QGroundControl software} %MDPI: Please state the version number of the software.
 for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped~\cite{qgroundcontrol}. Both the USV and UAV include long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network-attached storage to provide redundancy.

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\vspace{-0.1in}
\includegraphics[width=15.5cm]{figures/materials-and-methods/HyperSpectralInfoGraphic.pdf}
\end{adjustwidth}
\caption{A georectified reflectance data cube is visualized (center) with the $\log10$-reflectance along the z-axis and a pseudo-color image on the top. In the top left, we visualize the downwelling irradiance spectrum (the incident light). The surrounding plots showcase exemplar pixel reflectance spectra for open water, dry grass, algae, and a rhodamine dye plume used to test the system.\label{fig:hsi-infographic}}
\end{figure}

@@

For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data were randomly partitioned into a 90:10 training/testing split. To model the data, we chose to use the random forest regressor (RFR) as implemented in the machine learning framework for Julia package  \hl{MLJ} %MDPI: There is no ref {ben_sadeghi_2022_7359268}. Please check and revise.
%AE unsure if MLJ is an acronym and should thus be in parentheses
 \cite{decision-tree-julia, MLJ1}.  Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm. Each tree in an RFR is trained on a random subset of features \textit{\hl{and}} a random subset of training records \cite{decision-trees, random-forest}. Random forests are particularly attractive due to their fast training and inference times. Furthermore, studies continue to observe that tree-based models like random forest remain superior for tabular datasets \cite{grinsztajn2022tree, shwartz2022tabular}.

@@

Using these tools, the training procedure for each model was as follows: First, each model was trained using six-fold cross-validation on the full 526-feature training set with default hyperparameter values. Feature importances for the trained model were then computed, and the top 25 features were identified. A second model was then trained using the same six-fold cross-validation scheme with \textit{\hl{only}} these 25 most important features together with hyperparameter optimization using a random search over the number of trees and sampling fraction. The number of trees was optimized, as it has a significant impact on both model performance and inference time. The sampling ratio determines the fraction of training records that each individual tree is exposed to during training. Tuning this parameter helps limit overfitting by increasing the diversity of trees in the ensemble. Additionally, we chose to fix the maximum tree depth to 20 to control the final model size such that each trained model can fit in-memory on the onboard UAV processing computer. The remaining hyperparameters were left to their default values in order to constrain the total optimization space. The performance of each model was evaluated by computing out-of-fold scores for the coefficient of determination as well as the
\begin{align}
    \text{RMSE} &= \sqrt{\frac{\sum\limits_{i=1}^N (\hat{y}_i-y_i)^2}{N}}, \\
    \text{MAE} &= \frac{\sum\limits_{i=1}^N \lvert \hat{y}_i - y_i \vert}{N},
\end{align}
where RMSE is the root-mean-square error, and MAE is the mean absolute error between the true measurements $y_i$ and the predictions $\hat{y}_i$.

@@

\noindent 
\begin{tabular}{@{}ll}
GPS & Global Positioning System \\ 
INS & Inertial Navigation System \\
UTM & Universal Transverse Mercator \\
UV & Ultraviolet \\
ML & Machine Learning \\
USV & Uncrewed Surface Vessel \\
UAV & Unmanned Aerial Vehicle \\
CDOM & Colored Dissolved Organic Matter \\
CO & Crude Oil \\ 
OB & Optical Brighteners \\
FNU & Formazin Nephelometric Unit \\
RFR & Random Forest Regressor \\
RMSE & Root Mean Square Error \\ 
MAE & Mean Absolute Error \\
RENDVI & Red-Edge Normalized Difference Vegetation Index
\end{tabular}
}

@@

>>>>

 The robotic team presented in this study consists of two key sensing sentinels: an uncrewed surface vessel (USV) used to collect in situ reference measurements and an unmanned aerial vehicle (UAV) for performing rapid, wide-area surveys to gather remote sensing data products. Both platforms are coordinated using open-source QGroundControl version 4.0.11 software for flight control and mission planning and are equipped with high-accuracy GPS and INS such that all data points collected are uniquely geolocated and time-stamped~\cite{qgroundcontrol}. Both the USV and UAV include long-range Ubiquiti 5 GHz LiteBeam airMAX WiFi to enable streaming of data products to a ground station with network-attached storage to provide redundancy.

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\vspace{-0.1in}
\includegraphics[width=15.5cm]{figures/materials-and-methods/HyperSpectralInfoGraphic.pdf}
\end{adjustwidth}
\caption{A georectified reflectance data cube is visualized (center) with the $\log_{10}$ reflectance along the z-axis and a pseudo-color image on the top. In the top left, we visualize the downwelling irradiance spectrum (the incident light). The surrounding plots showcase exemplar pixel reflectance spectra for open water, dry grass, algae, and a rhodamine dye plume used to test the system.\label{fig:hsi-infographic}}
\end{figure}

@@

For each of the 13 target variables listed in Table~\ref{tab:sensors}, the data were randomly partitioned into a 90:10 training/testing split. To model the data, we chose to use the random forest regressor (RFR) as implemented in the Machine Learning framework for Julia (MLJ) \cite{random-forest-regression, MLJ1}.  Random forests are an ensembling technique based on bagged predictions of individual decision tree regressors trained using the classification and regression trees (CART) algorithm. Each tree in an RFR is trained on a random subset of features and a random subset of training records \cite{decision-tree, random-forest}. Random forests are particularly attractive due to their fast training and inference times. Furthermore, studies continue to observe that tree-based models like random forest remain superior for tabular datasets \cite{grinsztajn2022tree, shwartz2022tabular}.

@@

Using these tools, the training procedure for each model was as follows: First, each model was trained using six-fold cross-validation on the full 526-feature training set with default hyperparameter values. Feature importances for the trained model were then computed, and the top 25 features were identified. A second model was then trained using the same six-fold cross-validation scheme with only these 25 most important features together with hyperparameter optimization using a random search over the number of trees and sampling fraction. The number of trees was optimized, as it has a significant impact on both model performance and inference time. The sampling ratio determines the fraction of training records that each individual tree is exposed to during training. Tuning this parameter helps limit overfitting by increasing the diversity of trees in the ensemble. Additionally, we chose to fix the maximum tree depth to 20 to control the final model size such that each trained model can fit in-memory on the onboard UAV processing computer. The remaining hyperparameters were left to their default values in order to constrain the total optimization space. The performance of each model was evaluated by computing out-of-fold scores for the coefficient of determination as well as the
\begin{align}
    \text{RMSE} &= \sqrt{\frac{\sum\limits_{i=1}^N (\hat{y}_i-y_i)^2}{N}}, \\
    \text{MAE} &= \frac{\sum\limits_{i=1}^N \lvert \hat{y}_i - y_i \vert}{N},
\end{align}
where RMSE is the root-mean-square error, and MAE is the mean absolute error between the true measurements $y_i$ and the predictions $\hat{y}_i$.

@@

\noindent 
\begin{tabular}{@{}ll}
GPS & Global Positioning System \\ 
INS & Inertial Navigation System \\
UTM & Universal Transverse Mercator \\
UV & Ultraviolet \\
ML & Machine Learning \\
USV & Uncrewed Surface Vessel \\
UAV & Unmanned Aerial Vehicle \\
CDOM & Colored Dissolved Organic Matter \\
CO & Crude Oil \\ 
OB & Optical Brighteners \\
FNU & Formazin Nephelometric Unit \\
RFR & Random Forest Regressor \\
MLJ & Machine Learning framework for Julia \\
RMSE & Root Mean Square Error \\ 
MAE & Mean Absolute Error \\
RENDVI & Red-Edge Normalized Difference Vegetation Index
\end{tabular}
}

@@

\bibitem[Sadeghi et~al.(2022)Sadeghi, Chiarawongse, Squire, Jones, Noack, St-Jean, Huijzer, Schätzle, Butterworth, Peng, and Blaom]{random-forest-regression}
Sadeghi, B.; Chiarowongse, P.; Squire, K.; Jones, D.C.; Noack, A.; St-Jean, C.; Huijzer, R.; Schätzle, R.; Butterworth, I.; Peng, Y.; Blaom, A.
\newblock DecisionTree.jl - A Julia implementation of the CART Decision Tree and Random Forest algorithms.
\newblock {\em Zenodo} {\bf 2022}.
\newblock {\url{https://doi.org/10.5281/zenodo.7359268}}.
